surfing

### 2022-09-25 inst/surfing.Rmd
work on #171

>>>>

```{r, directplotofstengths}
pdf(file="directplotofstrengths.pdf")
par(xpd=NA)
plot(jjO,jjL,pch=16,log='y',xlab='points',ylab='maximum likelihood strength',cex=1.5)
fit <- lm(log10(jjL)~(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.8)
}
par(xpd=FALSE)
abline(fit)
dev.off()
```
